---
title: "popsheff"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

popsheff is an R package containing population data for Sheffield.

# Installation  

You can install the development version from GitHub with:

```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("scc-pi/popsheff")
```

If you work for Sheffield City Council you can install the binary package for Windows from:  

> S:\\BI Team\\ShareToAll\\RPackages

Using RStudio you can does this via the *Tools > Install packages...* menu.

# Source & format 

The data is from ONS. It has has been transformed into a [tidy data](https://r4ds.had.co.nz/tidy-data.html) format (or a tidier, longer format) so it is ready to use with [tidyverse](https://www.tidyverse.org/) R packages.

# Population data frames  

```{r library}
library(popsheff)
```

## LA (Local Authority) level

### pop_la_yrs

```{r pop_la_yrs}
head(pop_la_yrs)
```

### pop_la_median_age

```{r pop_la_median_age}
head(pop_la_median_age)
```

### pop_la_age

```{r pop_la_age}
head(pop_la_age)
```

### pop_la_age_male

```{r pop_la_age_male}
head(pop_la_age_male)
```

### pop_la_age_female

```{r pop_la_age_female}
head(pop_la_age_female)
```

## LAC (Local Area Committee) level

LAC boundaries are the same as ASC (Adult Social Care) localities.

### pop_lac_age

```{r pop_lac_age}
head(pop_lac_age)
```

### pop_lac_age_male

```{r pop_lac_age_male}
head(pop_lac_age_male)
```

### pop_lac_age_female

```{r pop_lac_age_female}
head(pop_lac_age_female)
```

## Ward level 

### pop_ward_age

```{r pop_ward_age}
head(pop_ward_age)
```

### pop_ward_age_male

```{r pop_ward_age_male}
head(pop_ward_age_male)
```

### pop_ward_age_female

```{r pop_ward_age_female}
head(pop_ward_age_female)
```

## LSOA level

### pop_lsoa_age_band

```{r pop_lsoa_age_band}
head(pop_lsoa_age_band)
```

